
\section{Introduction}

\subsection{Background}
\acrlong{nbim}, from now on referred to as \acrshort{nbim}, is a division within the central bank responsible for overseeing the Government Pension Fund of Norway, which has a worth of 13,000 billion Norwegian kroner \cite{nbimwebsite}. Due to its large value, the fund is a major target for potential malicious actors. It faces an average of three severe cyber attacks per day, totaling around 100,000 attacks each year. Out of these, more than 1,000 are considered significant threats \cite{nbimattacks}. Therefore, it is crucial for \acrshort{nbim}, as well as other organizations, to ensure the security of their systems and applications before deploying them into their cloud services. 

\acrlong{sdlc} (\acrshort{sdlc}), describes how software applications are built - from planning through implementation and running in production. It also includes ensuring security at the different stages of software development. In order to accommodate frequent deployments to production, it is important to automate the security testing by building it into the deployment pipeline. The security testing can further benefit from shift-left, where testing is done as early as possible in the pipeline. Given that source code can be accessed by anyone, it is important to consider potential vulnerabilities during the development process. Implementing a strong and secure software development life cycle is essential in preventing attacks from hackers and other malicious actors on your application 
\cite{sdlc}. Securing the \acrshort{sdlc} is a large and actively developed area with a lot of interest from the industry. Demonstrating the integration and practical application of various tools and methods can be beneficial for both \acrshort{nbim} and other organizations.
\subsection{Problema Area}
\subsection{Scope}
\subsection{Scope Limitation}
\subsection{Target group}
The thesis has different target groups. Our main target group will NBIM, which is our stakeholder for this thesis. They wanted us to make a general report about the task we were given from them, which could make it possible for other organization to to benefit from the findings we made in this report. Therefore, another target group will be other organizations who make use of the \acrshort{sdlc} and wants to secure it. 
\subsection{The Group’s Academic Background}
The project group is in the third and final year of a bachelor's degree in Digital Infrastructure and Cyber Security at the Norwegian University of Science and Technology (NTNU), campus Gjøvik. Throughout the study, the group have been through various subjects and subject areas such as risk management, ethical hacking and cybersecurity and teamwork - which all are subjects that has given the group knowledge that are relevant for the thesis. 
\subsection{Chapters}

