\section{Tools for testing}
\subsection{Introduction}
This chapter will give a description of the tools we determined to use. In addition, it will give an explanation to why we wanted to examine these specific tools further. 
\subsection{Astra}
Astra's Pentest suite uniquely combines automated vulnerability scanning with 3000+ tests and manual pentest by security experts to make security continuous and hassle-free for SMEs.It is a pentest platform for modern organisations with authenticated scanning, CI/CD integration, risk scoring, build-in collaboration, resolution center, and verifiable pentest. 

Astra Security tools are designed in a way that small and medium businesses without a dedicated security team can improve the security of applications with minimum technical requirements.You can start with the Automated DAST scanner to get the first security report of your web applications
certificates.
\subsection{Mend}
Mend effortlessly secures what developers create. Mend uniquely removes the burden of application security, allowing development teams to deliver quality, secure code, faster. Mend SCA is the market leader in securing the usage of open source in software development. It includes detecting, reporting, prioritizing, automatically remediating, and preventing open source risks.

Mend SAST provides custom code vulnerability detection and prioritization that enables developers to quickly and easily identify the most significant software risks in their proprietary code.

MEND Supply Chain Defender helps protect enterprises against software supply chain attacks. It detects and blocks malicious open source packages before your developer can download them and before they can pollute your codebase with malicious activity.


\subsection{Snyk}
Snyk is a developer security platform for securing code, dependencies, containers, and infrastructure as code. It scans your code, reads through it, and tells you if you have any vulnerabilities in your code.

Now it doesn't only check your code – it can check the installed dependencies, your Docker container, your Infrastructure as Code, and a few other things too.Snyk is compatible with a lot of languages and comes with plugins supported by different IDEs.
