\section{9 May 2023}
\textbf{Participants:} Anniken, Astri, Celina, Sebastian, Stian, Stian and Thea \\
\textbf{Time:} 14.00-14.50 \\
\textbf{Place:} Teams
\\~\\
\textbf{\underline{Discussion about the thesis - Structure}}
\begin{itemize}
    \item The thesis is very fragmented - maybe add some discussion before?
    \item Big change - we followed standard structure
    \item Example: which tool we chose, how to implement it, what we thought of it, all in one chapter?
    \item Out structure so far - introduce the theory, then present pipeline on a general basis without any specific tools, then the tools we use, and then how to implement it. Can read one without the other
    \item Talk about it with supervisor tomorrow
\end{itemize}

\textbf{\underline{Discussion about the thesis - Framework}}
\begin{itemize}
    \item Very detailed (reference to sections) - more curious on the overall assessment. 
    \item More highlevel discussion about if it is useful - consider work vs. utility
    \item Would we use it if we could choose? Or is it just more work?
\end{itemize}

\textbf{\underline{Discussion about the thesis - Conclusion}}
\begin{itemize}
    \item Other theses have had personal and theoretical conclusion combined, that is why we have it. Maybe a bit messy?
    \item Theoretical conclusion should maybe come after the theoretical discussion? 
\end{itemize}

\textbf{\underline{Discussion about the thesis - General}}
\begin{itemize}
    \item Should discuss where the practical part ended compared to the theoretical part
    \item Signing in Git but is not verified in AWS? 
    \item Verification should happen at every stage in the pipeline - not necessary where everything runs in the same stage
    \item Access control in the pipeline model - will maybe look messy to include one box for every stage. Maybe have a \say{global box} that refer to acccess control at every stage
    \item SAST and DAST in the pipeline model - only suggestions on where to have it. We only include it in one of the suggested stages
    \item SDLC phases - include that everything can be repeated. Takes time to set up first time, but is automated when repeated
    \item Deployment in the SDLC - more focused on automation, first time setup, reuse
    \item Scope limitation - perceived as apologetic
    \item Maybe look into SAST and DAST in consideration to AI?
    \item Astri did not experience SAST as easy to set up. Requires a lot of tweaking, get a lot of warnings
    \item We will set up Grammarly for help with academic writing
    \item Have sharpened the policies for the S3 bucket - no longer has access to everything
    \item Try to simplify the deploymetn chapter - only write about the necessary and important things, maybe include more code than text for some parts? Hard because there are so many components to set up for everything to work.
    \item Use footnotes more consistently 
\end{itemize}