\section{16 May 2023}
\textbf{Participants:} Anniken, Celina, Sebastian, Stian, Stian and Thea\\
\textbf{Time:} 14.00-14.30 \\
\textbf{Place:} Teams
\\~\\
\textbf{\underline{Discussion about the thesis}}
\begin{itemize}
    \item In the discussion, we have written that we are not making software, but the process is same as SDLC - Distinction of iac and application code, not necessary. The process of writing and developing, make it clear. 
    \item Phrase idempotent – professor thinks it is ok, they are not used to it, but since it is correct then its fine. Used in the context of iac 
    \item Table comparison – supervisor told us to change symbol for negative checks. We are leaving it as is. Specify “many false positives” for examples. 
    \item Read write permissions for CodePipeline – deploy only need read access. Can look at sharpening these permissions. Only add a comment, not spend too much time on it 
    \item The point of SDLC being iterative is fine 
    \item Chapter 5 is better and easier to understand now 
    \item Usefulness of the framework – added more feedback to it
    \item Most feedback now are small details 
    \item We need to fix abstract – need to make a good first impression
    \item Some details in the project plan - duplicate section and some small comments
    \item Why some code in appendix and other not? We have decided to have all code in GitHub, none in appendix. 
    \item Change some of the captions of the figured – more explanatory
\end{itemize}

\textbf{\underline{Other}}
\begin{itemize}
    \item If we need feedback – contact them directly, don’t need next meeting since delivery is on Monday 
    \item If they have time, maybe give us feedback in writing on what they think of our work, their view of the result and the process
    \item We can also give them feedback on what we think of the work with them - after delivery
\end{itemize}
