\section{16 May 2023}
\textbf{Participants:} Anniken, Celina, Filip, Sebastian and Thea\\
\textbf{Time:} 10.30-11.00 \\
\textbf{Place:} NTNU Campus Gjøvik, A221
\\~\\
 \textbf{\underline{Discussion about the thesis}}
 \begin{itemize}
     \item New title for chapter 5 - suggest \say{building a secure end-to-end pipeline} since that is what we do
     \item We are removing the code in the appendix and will just link to the different repositories in a footnote
        \begin{itemize}
            \item We have a GitHub organization with several repositories for different code purposes
        \end{itemize}
    \item Not necessary to link to the different CWEs from the alerts - also, refer to CVE from the theory
    \item Dependabot refers to a ghsa id, refers to GitHub Advisory Database, refers further to the same CVE id. Should we include? No, not necessary 
    \item Framework in discussion: have an introduction on what we want to do with it. Something in bold text in SLSA to be more consistent.
    \item Change \say{relevant hyperlink} to \say{code repository} or something 
    \item Keywords in abstract in alphabetical order 
    \item Rewrite some of the glossary entries, or add sources if it is directly taken from somewhere 
    \item Code when delivering – should we deliver the whole juice shop? We have made some small changes. 
        \begin{itemize}
            \item Only include the modified files, specify that it is the appspec file is our code and needs to be added to the juice-shop. Explain in the README file.
        \end{itemize}
 \end{itemize}




 

   